maxent model avec xvalidation (year-based test training)

### 2019-04-24 src/maxent_alldata_avec_xvalidation.Rmd
yup..

    #count number of non-zero coefficients, excluding the final four rows
    lambdas_list <- list.files(paste0("../output/maxent/p2/models/", timeslice), pattern = "*lambdas", full.names = TRUE)
    samppred_list <- list.files(paste0("../output/maxent/p2/models/", timeslice), pattern = "*samplePredictions.csv", full.names = TRUE)

>>>>

    #count number of non-zero coefficients, excluding the final four rows
    lambdas_list <- list.files(paste0("../output/maxent/", timeslice, "/models/"), pattern = "*lambdas", full.names = TRUE)
    samppred_list <- list.files(paste0("../output/maxent/", timeslice, "/models/"), pattern = "*samplePredictions.csv", full.names = TRUE)
